\section{Question 4}

\subsubsection*{Parameters}

\begin{itemize}
	\item $G = (N, A)$: the directed graph with nodes $N$ and arcs $A$.
	\item $d_k$: data to send from node $k \in N$.
	\item $c_i$: cost of installing devices at node $i \in N$.
	\item $cap_i$: capacity of devices installed at node $i \in N$.
	\item $T$: maximum allowed propagation time for data.
	\item $t_{ij}$: propagation delay on arc $(i, j) \in A$.
	\item $g_{ij}$: cost of installing channels on arc $(i, j) \in A$.
	\item $u$: capacity of each channel installed on arcs $(i, j) \in A$.
	\item $M_{ki}$: one if node $k \in N$ is reachable from node $i \in N$ through the shortest path, zero otherwise. If $d_k = 0$, then $M_{ki} = 0 \; \forall i \in N$.
\end{itemize}

\subsubsection*{Decision Variables}

\begin{itemize}
	\item $x_{ki}$ binary: one if data is sent from node $k$ to node $i$, zero otherwise.
	\item $y_i$ integer: number of devices installed at node $i$.
	\item $z_{ij}$ integer: number of channels installed on arc $(i, j)$.
	\item $w_{ij}^k$ binary: one if data from node $k$ is sent on arc $(i, j)$, zero otherwise.
\end{itemize}

\subsubsection*{Forced Variables}

\begin{itemize}
	\item $d_k = 0 \implies x_{kk} = 1 \quad \forall k \in N$
	\item $M_{ki} = 0 \implies x_{ki} = 0 \quad \forall k \in N, i \in N \mid j \ne i$
	\item $M_{ki} = 0 \vee M_{kj} = 0 \implies w_{ij}^k = 0 \quad \forall k \in N, (i, j) \in A$
\end{itemize}

\subsubsection*{Constraints}

\begin{enumerate}
	\item Each node must send its data to exactly one other node.
	\item For each node, enough devices must be installed to handle the data sent to it.
	\item For each arc, enough channels must be installed to handle the data sent on that arc.
	\item The propagation time must not exceed the maximum allowed time.
	\item Flow constraints: ensure that one and only one path from node $k$ to node $i$ exists if $x_{ki} = 1$; ensure that no data is sent on the network if a node sends data to itself ($x_{kk} = 1$).
\end{enumerate}

\subsubsection*{Model}

\begin{align*}
    \min \quad & \sum_{i \in N} c_i y_i + \sum_{(i, j) \in A} g_{ij} z_{ij} & \\
	\\
    \text{s.t.} \quad &  \\
	1. \quad & \sum_{i \in N \mid M_{ki} = 1} x_{ki} = 1 \qquad \forall k \in N \mid d_k > 0  \\
	2. \quad & \sum_{k \in N \mid M_{ki} = 1} d_k \; x_{ki} \le cap_i \; y_i \qquad \forall i \in N  \\
	3. \quad & \sum_{k \in N \mid M_{ki} = 1 \land M_{kj} = 1} d_k \; w_{ij}^k \le u \; z_{ij} \qquad \forall (i, j) \in A \quad  \\
	4. \quad & \sum_{(i, j) \in A \mid M_{ki} = 1 \land M_{kj} = 1} t_{ij} \; w_{ij}^k \le T \qquad \forall k \in N \mid d_k > 0  \\
	5. \quad & \sum_{(i, j) \in A \mid M_{kj} = 1} w_{ij}^k \; - \sum_{(j, i) \in A \mid M_{kj} = 1} w_{ji}^k = \left\{
	\begin{array}{rl}
		(1 - x_{kk}) & \text{if } i = k  \\
		-x_{ki} & \text{if } i \ne k
	\end{array}
	\right.
	\qquad \forall k \in N, \; i \in N \mid M_{ki} = 1  \\
	\\
	& x_{ki} \in \{0, 1\} \quad \forall k \in N, i \in N  \\
	& y_{ij} \in \mathbb{Z}^+ \quad \forall (i, j) \in A  \\
	& z_i \in \mathbb{Z}^+ \quad \forall i \in N  \\
	& w_{ij}^k \in \{0, 1\} \quad \forall k \in N, (i, j) \in A  \\
\end{align*}


\subsubsection*{Results}

\begin{table}[h!]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		\textbf{Instance} & \textbf{Optimal value} & \textbf{CPU time (s)} \\
		\hline
		1 & 85  & 0.095 \\
		\hline
		2 & 328 & 0.079 \\
		\hline
		3 & 376 & 0.039 \\
		\hline
		4 & 149 & 3.225 \\
		\hline
		5 & 154 & 0.543 \\
		\hline
		6 & 424 & 13.843 \\
		\hline
		7 & 420 & 10.754 \\
		\hline
	\end{tabular}
	\label{tab:instance_costs}
\end{table}
